---
title: "Exercise #3"
subtitle: "Fortgeschrittene Statistische Software für NF"
author: "Jonas Peter (12552802), Moritz Dresch (12579171)"
date: "`r Sys.Date()`"
output: distill::distill_article
---

## Exercise 1: Initializing git (4 Points)

### Exercise 1d: 
#### Strengths of Git: 
#### 1.: Distributed Version Control
#### 2.: Branching and Merging
#### Weaknesses of Git:
#### 1.: Complexity for Beginners
#### 2.: Potential for Conflicts

## Exercise 2: Putting your Repository on GitHub (3.5 Points)

### Exercise 2a,b,c: 
https://github.com/jpeter96/exeRcise-sheet-3

## Exercise 3: Baby-Names in Munich (3.5 Points)

### Exercise 3a,b,c:
```{r}
library(dplyr)
library(readr)
library(knitr)
install.packages("kableExtra")
library(kableExtra)
library(ggplot2)

data_2022 <- read_csv("data/open_data_portal_2022.csv")
data_2023 <- read_csv("data/vornamen-muenchen-2023.csv")

str(data_2022)
str(data_2023)

summary(data_2022$Anzahl)
summary(data_2023$Anzahl)

# Identify non-numeric entries in the count variable
unique(data_2022$Anzahl[!grepl("^[0-9]+$", data_2022$Anzahl)])
unique(data_2023$Anzahl[!grepl("^[0-9]+$", data_2023$Anzahl)])

# Convert the count variable to numeric, replacing non-numeric entries with NA
data_2022$Anzahl <- as.numeric(gsub("[^0-9]", "", data_2022$Anzahl))
data_2023$Anzahl <- as.numeric(gsub("[^0-9]", "", data_2023$Anzahl))

summary(data_2022$Anzahl)
summary(data_2023$Anzahl)

# Calculate the total number of babies born each year
total_babies_2022 <- sum(data_2022$Anzahl, na.rm = TRUE)
total_babies_2023 <- sum(data_2023$Anzahl, na.rm = TRUE)

# Print the results
total_babies_2022
total_babies_2023
```
### Exercise 3d:
```{r}
data_2022 <- data_2022 %>%
  mutate(year = 2022)

data_2023 <- data_2023 %>%
  mutate(year = 2023)

head(data_2022)
head(data_2023)
```
### Exercise 3e:
```{r}
combined_data <- bind_rows(data_2022, data_2023)

head(combined_data)
```
### Exercise 3f:
```{r}
combined_data$Anzahl <- as.numeric(gsub("[^0-9]", "", combined_data$Anzahl))

combined_counts <- combined_data %>%
  group_by(Vorname) %>%
  summarize(Total_Anzahl = sum(Anzahl, na.rm = TRUE)) %>%
  arrange(desc(Total_Anzahl))

top_10_names <- combined_counts %>%
  head(10)

kable(top_10_names, caption = "Top 10 Most Popular Baby Names in Munich (2022 & 2023)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```
## Exercise 4: Open Analysis (4 points)

### Exercise 4a,b,c:
-   Dataset Name: CO2 emissions by source - CDIAC (2016)
-   Link: <https://github.com/owid/owid-datasets/blob/master/datasets/CO2%20emissions%20by%20source%20-%20CDIAC%20(2016)/CO2%20emissions%20by%20source%20-%20CDIAC%20(2016).csv>...
```{r}
co2_data <- read_csv("data/CO2-emissions-by-source-CDIAC_2016.csv")

head(co2_data)

summary(co2_data)

str(co2_data)
```
### Exercise 4d:
Research Question: How has the distribution of CO2 emissions from various sources evolved over time, and what are the main contributors to global CO2 emissions?
This question is interesting because it is becoming more relevant by the day as our global climate is warming and CO2 is a leading cause-factor. 

### Exercise 4e:
```{r}
co2_data <- co2_data %>%
  mutate(total_emissions = `Solid fuel consumption (CDIAC (2016))` + 
                            `Liquid fuel consumption (CDIAC (2016))` +
                            `Gas fuel consumption (CDIAC (2016))` +
                            `Cement production (CDIAC (2016))` +
                            `Gas flaring (CDIAC (2016))`)

head(co2_data)
```
### Exercise 4f:
```{r}
co2_data <- co2_data %>%
  na.omit()

ggplot(co2_data, aes(x = Year, y = total_emissions, color = Entity)) +
  geom_line() +
  labs(title = "Total CO2 Emissions Over Time",
       x = "Year",
       y = "Total CO2 Emissions (metric tons)")
```

